---
title: "WGCATCH 2025, ToR c BYC inventory"
author: "Karolina, Sarah"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r}
# PACKAGES
library(tidyverse, quietly = TRUE)
library(DT)
library(readxl)
library(gridExtra)
library(paletteer)
library(ggpubr)
library(patchwork)
library(ggokabeito)
```





### Coverage by sampling scheme


```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))

# Without 0's
yearsCellWTZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```

### Coverage by sampling effort
```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))

# Without 0's
yearsCellWTZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled )) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```

### Comparison with CE

```{r, fig.dim= c(16, 12)}
dfnornew <- filter(dfnor, Source %in% "2025DC") %>%
  filter(Year >= 2021 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0)
cemerg <- left_join(cef, dfnornew, by = c("AreaCode" = "AreaCode2", "GearGroup" = "GearGroup1"))

cefin <- distinct(cemerg, AreaCode, GearGroup, .orig_row) %>%
  mutate(Sampled = ifelse(is.na(.orig_row), "No", "Yes")) %>%
  distinct(AreaCode, GearGroup, Sampled) %>%
   mutate(GearGroup = factor(GearGroup, levels = c("DemTrawl", "DemSeine","Gillnetters", "LinesHooks", "PelSeine", "PelTrawl", "Others")),
          AreaCode = factor(AreaCode, levels = unique(ices_divisions$division)))


ggplot(cefin , aes(x = GearGroup, y = AreaCode, fill = Sampled)) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "SAmpled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Year * gear combination sampled"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```



## Med

### Coverage by year

```{r, fig.dim= c(16, 12)}

# Factors to be plotted in order
dfmed<- med  %>%
  mutate(AreaCode2 = factor(AreaCode, levels = paste0("GSA ", seq(1:30))),
         GearGroup1 = factor(GearGroup, levels = c("DemTrawl", "DemSeine","Gillnetters", "LinesHooks", "PelSeine", "PelTrawl", "Others")))

# Remove NAFO areas
dfmed <- filter(dfmed, !is.na(AreaCode2))

# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  filter(is.na(GearGroup1) == F) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoYears = length(unique(Year)))

# Without 0's
yearsCellWTZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(is.na(GearGroup1) == F) %>%
  filter(NoTripsSampled != 0) %>%
  filter(is.na(NoTripsSampled) == F) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoYears = length(unique(Year)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoYears))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Years") +
  labs(
    x = "Gear",
    y = "GSA",
    title = "Unique year coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoYears))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Years", alpha = 0.85) +
  scale_x_discrete(labels = c("Demersal Trawl", "Demersal Seine", "Gilnetters", "Lines and Hooks", "Pelagic Seine", "Pelagic Trawl", "Other"))+
  labs(
    x = "Gear group",
    y = "Geographical sub-area (GSA)",
    title = "Years of coverage by gear group and GFCM geographical sub-area (2017-2024)"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

Fig4 <- b

grid.arrange(a, b, ncol=2)

Fig4

ggsave("Fig4.png", Fig4, width = 20.5, height = 10, units = "cm", dpi = 300)
```

### Coverage by sampling scheme

```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))

# Without 0's
yearsCellWTZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "GSA",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "GSA",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```


### Coverage by sampling effort

```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))

# Without 0's
yearsCellWTZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled )) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```


```{r}
d4samType <- d4 %>%
  group_by(SamplingScheme,MonitoringMethod) %>%
  summarise(Samname = paste0(unique(SamplingSchemeType), collapse = ","))

```

#Some general patterns over time

```{r}
#calculate range of programs
#use only data from this year's call
d4e <- d4 %>%
  mutate(End_year = replace(End_year, is.na(End_year) == T,2025)) %>%
  mutate(End_year = replace(End_year, End_year == 2026 | End_year == 2027, 2025)) %>%
  mutate(range = End_year - Start_year) %>%
  mutate(Start_year = replace(Start_year, Start_year <2017, 2016)) %>%
  mutate(range = End_year - Start_year +1) %>%
  mutate(Start_year = replace(Start_year, Start_year <2017, "<2017"))

#filter for unique programs
d4_unique <- d4e %>% dplyr::select(Start_year,End_year,SamplingScheme,range, SamplingSchemeType,MonitoringMethod, AreaCode, TargetPopulation) %>%
  distinct()

#histogram of program lengths
ggplot(d4e)+
  geom_bar(aes(range, fill = SamplingSchemeType), color = "darkgrey",stat = "count")+
  labs(x = "Number of years", y = "Number of programmes", title = "Duration of bycatch monitoring programmes")+
  scale_y_continuous(expand = c(0,0))+
  theme_classic()


# #pull out columns of interest
# d4e_sub <- d4 %>%
#   filter(!MonitoringMethod == "LB") %>%
#   mutate(End_year = replace(End_year, is.na(End_year) == T,2025)) %>%
#   mutate(End_year = replace(End_year, End_year == 2026 | End_year == 2027, 2025)) %>%
#   filter(Start_year > 2016) %>%
#   mutate(range = End_year - Start_year +1) %>%
#   dplyr::select(Start_year,End_year,SamplingScheme,range, SamplingSchemeType,MonitoringMethod,AreaCode)

#expanded data frame for each year
# d4_byyear <- c()
# for(i in 1:length(d4e_sub$Start_year)) {
#   program <- d4e_sub[i,] #pull out unique program
#   temp <- as.data.frame(matrix(ncol = ncol(d4e_sub) + 1,nrow = program$range))
#   colnames(temp) <- c(colnames(d4e_sub),"Year")
#   temp$Year <- seq(program$Start_year,program$End_year,1)
#   temp[,1:ncol(d4e_sub)] <- program
#   d4_byyear <- rbind(d4_byyear,temp)
# }
#
# #time series of program type by monitoring method
# #MINDFUL THAT WE KNOW THERE ARE ZEROS! Probably not good to do this
# d4_byyear %>%
#   #filter(zero == "no") %>%
# ggplot() +
#   geom_bar(aes(x = Year, fill = MonitoringMethod), position = "stack") +
#   scale_x_continuous(breaks = seq(2017,2025, by = 1), expand = c(0,0)) +
#   scale_y_continuous(expand = c(0,0))+
#   theme_classic()

#time series of program type by program type
# d4_byyear %>% filter(zero == "no") %>%
# ggplot() +
#   geom_bar(aes(x = Year, fill = SamplingSchemeType), position = "stack") +
#   scale_x_continuous(breaks = seq(2017,2025, by = 1), expand = c(0,0)) +
#   scale_y_continuous(expand = c(0,0))+
#   theme_classic()

labels <- c("<2017", seq(2017,2025, by = 1))

#time series of programs by type and start year
Fig1 <- ggplot(data = d4e) +
  geom_bar(aes(x = Start_year, fill = SamplingSchemeType), position = "stack", color = "black") +
  scale_x_discrete(breaks = labels) +
  scale_fill_okabe_ito(alpha = 0.75)+
  scale_y_continuous(expand = c(0,0))+
  labs(x = "Initial year", y = "Number of programmes", fill = "Programme Type")+
  theme_classic()


Fig1

ggsave("Fig1.png", Fig1, width = 20, height=10, units=c("cm"), dpi=300)

#time series of programs bysea_star#time series of programs by method and start year
Fig2<- ggplot(data = d4e) +
  geom_bar(aes(x = Start_year, fill = MonitoringMethod), position = "stack", color = "black") +
  scale_x_discrete(breaks = labels) +
  #scale_fill_viridis_d(direction = -1)+
  scale_fill_okabe_ito(alpha = 0.75)+
  scale_y_continuous(expand = c(0,0))+
  labs(x = "Initial year", y = "Number of programmes", fill = "Method")+
  theme_classic()

Fig2

ggsave("Fig2.png", Fig2, width = 20, height=10, units=c("cm"), dpi=300)

```
#Percentage of programs with Sci. Observers
```{r}
#percentage of programs with SO
so <- length(which(d4e$MonitoringMethod %in% c("SO","SO~PO","SO~VO")))
so/length(d4e$MonitoringMethod)

#number of countries utilizing EM
em <- d4e %>% filter(MonitoringMethod == "EM") %>%
  select(Country) %>%
  distinct()
```
#Exclusion criteria
```{r}
#looking at exclusion criteria
exclusion <- d4e %>% filter(ExclusionFlag == "Y") %>%
  filter(is.na(ExclusionCriteria) == F) %>%
  mutate(ExclusionCriteria = replace(ExclusionCriteria, ExclusionCriteria == "low fishing effort", "Low fishing effort")) %>%
  mutate(ExclusionCriteria = replace(ExclusionCriteria, ExclusionCriteria == "Vessel space limitation~Uncooperative vessel", "Uncooperative vessel~Vessel space limitation")) %>%
  mutate(ExclusionCriteria = replace(ExclusionCriteria, ExclusionCriteria == "Small vessel size~Vessel space limitation~Low fishing effort", "Small vessel size~Low fishing effort~Vessel space limitation"))

Fig7 <- ggplot(data = exclusion) +
  geom_bar(aes(x= "", fill = ExclusionCriteria), color = "black")+
  labs(fill = "Exclusion Critera")+
  coord_polar("y", start = 0)+
  scale_fill_okabe_ito(alpha = 0.75)+
  theme_void()

Fig7

ggsave("Fig7.png", Fig7, width = 20, height=8, units=c("cm"), dpi=300)

#curious about how many exclusions relate to uncooperative
length(which(exclusion$ExclusionCriteria %in% c("Uncooperative vessel", "Uncooperative vessel~Vessel space limitation", "Uncooperative vessel~Small vessel size")))
```

#Sampling protocols (species sampled)
```{r}
#looking at sampling protocols
d4e <- d4e %>% filter(!MonitoringMethod == "LB")
Fig5a <- ggplot(data = d4e) +
  geom_bar(aes(x= "", fill = SamplingProtocol), color = "black")+
  scale_fill_okabe_ito(alpha = 0.75, order = c(7:9,1:6))+
  coord_polar("y", start = 0)+
  labs(fill = "Sampling Protocol")+
  theme_void()

#proportion that sample 'All' and 'Protected Species'
length(which(d4$SamplingProtocol == "All"))/length(d4$SamplingProtocol)
length(which(d4$SamplingProtocol == "ProtectedSpecies"))/length(d4$SamplingProtocol)

Fig5b <- ggplot(data = d4e) +
  geom_bar(aes(x=SamplingSchemeType, fill = SamplingProtocol),position = "fill", show.legend = F, color = "black") +
  scale_x_discrete(expand = c(0,0)) +
 scale_fill_okabe_ito(alpha = 0.75, order = c(7:9,1:6))+
  scale_y_continuous(expand = c(0,0))+
  labs(y = "Proportion", x= "Programme Type")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust = 1))

specific <- d4e %>% filter(!SamplingProtocol %in% c("All", "ProtectedSpecies", "Fish~ProtectedSpecies", "ProtectedSpecies~Elasmobranchs")) %>%
  count(SamplingProtocol)

Fig5 <- Fig5a + Fig5b + plot_annotation(tag_levels = "A")

Fig5

ggsave("Fig_5.png", Fig5, width = 25, height = 10, units = "cm", dpi = 300)
```
#Monitoring coverage
```{r}
#exclude logbook programs
lb <- d4 %>% filter(MonitoringMethod == "LB")
#look at monitoring coverage relative to thresholds
hist <- d2 %>% mutate(prop = NoTripsSampled / NoTripsTotal) %>%
  filter(!SamplingScheme %in% lb$SamplingScheme) %>%
  filter(prop > 0 & prop <1)

Fig8 <- ggplot(data = hist) +
  geom_histogram(aes(x=prop), fill = "lightgrey", color = "black", binwidth = 0.01) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0))+
  geom_vline(xintercept=0.01, color="orange", linetype = "dashed", linewidth = 1)+
  annotate(x= 0.01, y=+Inf,label = "0.01",vjust = 7, hjust=-0.0001, geom = "label", color = "orange", size = 11/.pt)+
   geom_vline(xintercept=0.1, color="maroon", linetype = "dashed", linewidth = 1)+
  annotate(x= 0.1, y=+Inf,label = "0.1",vjust = 7, hjust=-0.0001,geom = "label", color = "maroon",size = 11/.pt)+
   labs(x = "Proportion", title = "Proportion of fishing trips sampled (2022-2025)", y = "Number of programmes") +
  theme_classic()
Fig8

ggsave("Fig8.png", Fig8, width = 20, height = 10, units = "cm", dpi = 300)

#what % of schemes are below 10% threshold
length(which(hist$prop < 0.1)) / length(hist$prop)

#what % of schemes are below 0.1% threshold
length(which(hist$prop < 0.001)) / length(hist$prop)

#what % of schemes are below 10% threshold
length(which(hist$prop < 0.01)) / length(hist$prop)

#how does prop relate to total trips
ggplot(data = hist) +
  geom_point(aes(y= NoTripsTotal, x= prop))
```

Programs that report zeros

```{r}
#noticed a lot of NAs as well
d2e <- d2e %>% mutate(NoTripsSampled = replace(NoTripsSampled, is.na(NoTripsSampled) == T, 0))

zeros <- d2e %>% filter(NoTripsSampled == 0)

#plot by year and by country
#France mostly!
ggplot(data = zeros) +
  geom_bar(aes(x = Year, fill = Country))


#are there cases where a program reports zeros in a year
#Yes, 84 instances
trips_annual <- d2e %>% group_by(SamplingScheme,Year) %>%
  mutate(annual_trips = sum(NoTripsSampled)) %>%
  dplyr::select(SamplingScheme,Year,annual_trips,Country) %>%
  distinct()

zeros <- zeros %>% mutate(unique_ID = paste(SamplingScheme,AreaCode,Year, sep = "_"))

d4_byyear <- d4_byyear %>% mutate(unique_ID = paste(SamplingScheme,AreaCode,Year, sep = "_"))

d4_byyear <- d4_byyear %>% mutate(zero = ifelse(unique_ID %in% zeros$unique_ID, "yes","no"))

```

#Perceived importance issues
```{r}
#mean range of CF vs. IB
#function to pull last two letters (=CF or IB)
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

#classify by either CF or IB
d4e <- d4e %>% mutate(SST = substrRight(SamplingSchemeType,2))

d4_importance <- d4e %>% group_by(SST) %>%
  mutate(Mammals = mean(ImportanceMammals), Birds = mean(ImportanceBirds), Fish = mean(ImportancePETfish), Elasmobranchs = mean(ImportanceElasm), Reptiles = mean(ImportanceRept)) %>%
  dplyr::select(SST, Mammals, Birds, Fish, Elasmobranchs, Reptiles) %>% distinct()

d4_importance <- pivot_longer(d4_importance, !SST, names_to = "Taxon", values_to = "Importance")

Fig6<- ggplot(data = d4_importance) +
  geom_bar(aes(x = Taxon, y = Importance, fill = SST), stat = "identity", position = "dodge", color = "black") +
  labs(x = "", y = "Average perceived importance (0-4)", title = "Perceived importance of fishery monitored, relative to other fisheries, for the bycatch of different taxonomic groups", fill = "Sampling Scheme Type") +
  scale_fill_okabe_ito(alpha = 0.75,labels = c("Commercial fisheries", "Incidental bycatch"))+
  #scale_fill_discrete(palette = c(pal[6],pal[5]),labels = c("Commercial fisheries", "Incidental bycatch"))+
  scale_y_continuous(expand = c(0,0))+
  theme_classic()

Fig6

ggsave("Fig6.png", Fig6, width = 25, height = 10, units = "cm", dpi = 300)
```

#Part observed
```{r}
part_observed <- d4 %>% group_by(PartObserved) %>% tally()
length(which(grepl("So", d4$PartObserved) == T))

```
