---
title: "WGCATCH 2025, ToR c BYC inventory"
author: "Karolina, Sarah"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r}
# PACKAGES
library(tidyverse, quietly = TRUE)
library(DT)
library(readxl)
library(gridExtra)
library(paletteer)
library(ggpubr)
library(patchwork)
library(ggokabeito)
```


```{r}
# Useful fun
classify_gear <- function(x) {

  # capture the NAs
  if (is.na(x)) return(NA_character_)

  # split on underscores and treat each piece as a separate code
  parts <- unlist(str_split(x, "_"))
  parts <- parts[str_detect(parts, "^[A-Za-z]+$")]

  # helper for standalone-ish match
  tok <- function(x) paste0("(?<![A-Z])(", x, ")(?![A-Z])")

  cats <- c(
    PelTrawl = any(str_detect(parts, regex(tok("OTM|PTM|PT"), ignore_case = TRUE))),
    DemTrawl = any(str_detect(parts, regex(tok("OTB|PTB|TBB|OTT|TB"), ignore_case = TRUE))),
    DemSeine = any(str_detect(parts, regex(tok("SSC|SPR|SDN"), ignore_case = TRUE))),
    PelSeine = any(str_detect(parts, regex(tok("PS"), ignore_case = TRUE))),
    LinesHooks = any(str_detect(parts, regex(tok("LLD|LLS|LH|LHP|LHM|LTL"), ignore_case = TRUE))),
    Gillnetters = any(str_detect(parts, regex(tok("GNS|GTR|GN|GND|GTN|GNC"), ignore_case = TRUE)))
  )

  # free-text rules look at full string
  cats["PelTrawl"]    <- cats["PelTrawl"]    | str_detect(x, regex("pelagic trawler", ignore_case = TRUE))
  cats["Gillnetters"] <- cats["Gillnetters"] | str_detect(x, regex("gillnetter", ignore_case = TRUE))
  cats["DemTrawl"]    <- cats["DemTrawl"]    | (str_detect(x, regex("trawler", ignore_case = TRUE)) &
                                                 str_detect(x, regex("demersal|cod", ignore_case = TRUE)))

  present <- names(cats)[cats]

  if (length(present) == 0) {
    "Others"
  } else if (length(present) == 1) {
    present
  } else {
    paste0("Multiple (", paste(sort(present), collapse = "+"), ")")
  }
}

# Expand area
expandIcesArea <- function(x) {
  x <- str_replace_all(x, " ", "")
  x <- str_replace(x, "\\.$", "")   # drop dot

  # Pure 27 region or fully specified already
  if (x == "27") return(x)
  if (str_detect(x, "^27\\.[0-9]+(\\.[A-Za-z0-9]+)*$")) return(x)

  # 27.4b, 27.7bcjk
  if (str_detect(x, "^27\\.[0-9]+[A-Za-z]+$")) {
    num     <- str_match(x, "^27\\.([0-9]+)")[, 2]
    letters <- str_match(x, "^27\\.[0-9]+([A-Za-z]+)$")[, 2]
    letters_vec <- strsplit(letters, "")[[1]]
    letters_vec <- letters_vec[letters_vec != ""]
    return(sprintf("27.%s.%s", num, letters_vec))
  }

  # 7bcjk, 7fgh etc
  if (str_detect(x, "^[0-9]+[A-Za-z]+$")) {
    num     <- str_match(x, "^([0-9]+)")[, 2]
    letters <- str_match(x, "^[0-9]+([A-Za-z]+)$")[, 2]
    letters_vec <- strsplit(letters, "")[[1]]
    letters_vec <- letters_vec[letters_vec != ""]
    return(sprintf("27.%s.%s", num, letters_vec))
  }

  # 27.1, 27.12 etc keep as is will be expanded
  if (str_detect(x, "^27\\.\\d+$")) return(x)

  # Fallback: keep unchanged
  x
}

# Parse
parse_one_code <- function(code) {
  orig <- code

  code <- str_squish(code)

  if (is.na(code) || code == "" || code == "NA") {
    return(tibble(
      original       = orig,
      AreaCode_system = NA_character_,
      AreaCode        = NA_character_
    ))
  }

  # Split on both "~" and "," (mixed strings)
  parts <- str_split(code, "[~,]")[[1]] %>%
    str_squish()

  parts <- parts[parts != ""]

  map_dfr(parts, function(p) {
    if (is.na(p) || p == "") {
      return(tibble(
        original        = orig,
        AreaCode_system = NA_character_,
        AreaCode        = NA_character_
      ))
    }

   #  explicit GSA + number
    if (str_detect(str_to_upper(p), "^GSA\\s*\\d+$")) {
      num <- as.integer(str_extract(p, "\\d+"))
      return(tibble(
        original        = orig,
        AreaCode_system = "GSA",
        AreaCode        = paste0("GSA ", num)
      ))
    }

    # Plain digits
    if (str_detect(p, "^\\d{1,2}$")) {
      # If original string has a 27.* and no 'GSA'  interpret as 27.<n> (like 27.12,14)
      if (str_detect(orig, "27\\.") &&
          !str_detect(orig, regex("\\bGSA\\b", ignore_case = TRUE))) {
        new_code <- paste0("27.", p)
        return(tibble(
          original        = orig,
          AreaCode_system = "ICES",
          AreaCode        = new_code
        ))
      } else {
        # Otherwise treat as GSA number
        num <- as.integer(p)
        return(tibble(
          original        = orig,
          AreaCode_system = "GSA",
          AreaCode        = paste0("GSA ", num)
        ))
      }
    }

    p_clean <- str_replace_all(p, " ", "")
    p_clean <- str_replace(p_clean, "\\.$", "")

    if (str_detect(p_clean, "^27(\\.|$)") ||
        str_detect(p_clean, "^[0-9]+[A-Za-z]+$")) {
      expanded <- expandIcesArea(p_clean)
      # expanded may be length > 1
      return(tibble(
        original        = orig,
        AreaCode_system = "ICES",
        AreaCode        = expanded
      ))
    }

    # Unknown stuff
    tibble(
      original        = orig,
      AreaCode_system = "Unknown",
      AreaCode        = p
    )
  })
}

#

```

```{r}
# Bind the d2
d2 <- mutate(d2, Source = "2025DC")
d2old <- mutate(d2old,
                NoTripsSampled = as.numeric(NoTripsSampled),
                NoTripsTotal = as.numeric(NoTripsTotal),
                Source = "2020DC")
d2all<- bind_rows(d2, d2old)

# mutate PT-20 to PT and the two codes for Germany
d2all <- mutate(d2all, Country = ifelse(Country %in% "PT-20", "PT",
                                        ifelse(Country %in% "DEU", "DE", Country)))

```



# Overview

Number of countries responded in the 2020 and 2025 datacall respectively.

```{r}
d2Tab <- d2all %>%
  group_by(Source) %>%
  summarise(NoCountries = length(unique(Country)),
            Countries = paste0(sort(unique(Country)), collapse = ", "))

d2Tab  %>%
  datatable(extensions = 'Buttons', rownames = FALSE,
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


# Data cleaning

## Gear/Metier groupings

The metiers reported by each country were grouped into six categories:

1. Pelagic trawl
2. Demersal trawl
3. Demersal seine
4. Pelagic seine
5. Lines and hooks
6. Others

The table below shows how metiers were grouped to the categories above:


```{r}
# Group metiers - inventories

d2allg <- d2all %>%
  separate_rows(Gear, sep = "[,;/]\\s*") %>%
  mutate(Gear = str_trim(Gear),
         GearGroup = vapply(Gear, classify_gear, character(1)))
tabgear <- distinct(d2allg, Gear, GearGroup)
tabgear %>%
  datatable(extensions = 'Buttons', rownames = FALSE,
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
# Group gears - CE - run at the end its taking too long
# ce <- mutate(ce, GearGroup = vapply(CEmetier6, classify_gear, character(1))) # takes too long
# tabgearce <- distinct(ce, CEmetier6, GearGroup)
# datatable(tabgearce, caption = "Grouped metiers in the old datacall")
```


```{r}
# Look up table
ices_divisions <- tribble(
  ~subarea,   ~division,
  # 27.1
  "27.1",     "27.1.a",
  "27.1",     "27.1.b",
  # 27.2
  "27.2",     "27.2.a",
  "27.2",     "27.2.b",
  # 27.3 (Baltic + Kattegat)
  "27.3.a",   "27.3.a.20",
  "27.3.a",   "27.3.a.21",
  "27.3.b",   "27.3.b.23",
  "27.3.c",   "27.3.c.22",
  # 27.3.d (Baltic Proper) incl. 28.1/28.2
  "27.3.d",   "27.3.d.24",
  "27.3.d",   "27.3.d.25",
  "27.3.d",   "27.3.d.26",
  "27.3.d",   "27.3.d.27",
  "27.3.d",   "27.3.d.28",
  "27.3.d",   "27.3.d.28.1",
  "27.3.d",   "27.3.d.28.2",
  "27.3.d",   "27.3.d.29",
  "27.3.d",   "27.3.d.30",
  "27.3.d",   "27.3.d.31",
  "27.3.d",   "27.3.d.32",
  # 27.4 (North Sea)
  "27.4",     "27.4.a",
  "27.4",     "27.4.b",
  "27.4",     "27.4.c",
  # 27.5 (Iceland & Faroes)
  "27.5",     "27.5.a",
  "27.5",     "27.5.b",
  # 27.6 (W of Scotland/Rockall)
  "27.6",     "27.6.a",
  "27.6",     "27.6.b",
  "27.6.b",   "27.6.b.1",
  # 27.7 (Celtic/Biscay)
  "27.7",     "27.7.a",
  "27.7",     "27.7.b",
  "27.7",     "27.7.c",
  "27.7",     "27.7.d",
  "27.7",     "27.7.e",
  "27.7",     "27.7.f",
  "27.7",     "27.7.g",
  "27.7",     "27.7.h",
  "27.7",     "27.7.j",
  "27.7",     "27.7.k",
  # 27.8 (Bay of Biscay)
  "27.8",     "27.8.a",
  "27.8",     "27.8.b",
  "27.8",     "27.8.c",
  "27.8",     "27.8.d",
  "27.8",     "27.8.e",
  # 27.9
  "27.9",     "27.9.a",
  "27.9",     "27.9.b.1",
  "27.9",     "27.9.b.2",
  "27.9",     "27.9.b",
  # 27.10 (Azores)
  "27.10",    "27.10.a",
  "27.10.a",  "27.10.a.1",
  "27.10.a",  "27.10.a.2",
  "27.10",    "27.10.b",
  # 27.12 (Svalbard/Barents fringe)
  "27.12",    "27.12.a",
  "27.12",    "27.12.b",
  "27.12",    "27.12.c",
  # 27.14 (Greenland)
  "27.14",    "27.14.a",
  "27.14",    "27.14.b"
)
```

```{r}

# Collapse list cols, keep original row
d2e <- d2allg %>%
  ungroup() %>%
  mutate(.orig_row = row_number()) %>%
  rowwise() %>%
  mutate(
    AreaCode_collapsed = paste(AreaCode, collapse = "~")
  ) %>%
  ungroup()

# Expand general
d2_expanded <- d2e %>%
select(-AreaCode) %>%
  mutate(parsed = map(AreaCode_collapsed, parse_one_code)) %>% # the error is in the nested functions above, not here
  unnest(parsed) %>%
  # clean up
  select(-AreaCode_collapsed)

# Expand subarea -> subdiv
d2div <- d2_expanded %>%
  mutate(
    AreaCode = str_trim(AreaCode)   # just in case there are stray spaces
  ) %>%
  left_join(ices_divisions, by = c("AreaCode" = "subarea")) %>%
  mutate(
    # if AreaCode matches a subarea in the lookup, use that division,
    # otherwise keep the original AreaCode
    AreaCode1 = if_else(!is.na(division), division, AreaCode)
  ) %>%
  select(-division) %>%
  distinct(.orig_row, AreaCode1, AreaCode_system, .keep_all = TRUE)

```


```{r}
# Fix specific stuff
d2div <- mutate(d2div, AreaCode = ifelse(AreaCode %in% "37.2.1", "GSA 17", AreaCode))
# Exclude 3271 France (talked with Sebastien)
# Exclude 27.3.bc
d2div <- filter(d2div, !(AreaCode %in% "3721" & Country %in% "FR"& Source %in% "2025DC"))
d2div <- filter(d2div, !(AreaCode %in% "27.3.bc" & Country %in% "FR"& Source %in% "2025DC"))
# Reassign 3.a to 4.b (rectangle ovelap issue)
d2div <- mutate(d2div, AreaCode = ifelse(Country %in% "FR" & AreaCode %in% "27.3.a"& Source %in% "2025DC", "27.4.b", AreaCode))

# Exclude Finland area 27.3.d. (all Baltic) - Email for new submission: Done
# d2div <- filter(d2div, !AreaCode %in% "27.3.d.")

# Fix Slovenia
d2div <- mutate(d2div, AreaCode_system = ifelse(Country %in% "SI", "GSA", AreaCode_system))


# Several records in the old datacall don't have area
naArea <- filter(d2div, is.na(AreaCode))
d2div <- filter(d2div, !is.na(AreaCode))
```


```{r}
d2div <- d2div %>%
  mutate(AreaCode = ifelse(substr(AreaCode1, 1, 4) == "27.3", substr(AreaCode1, 1, 9), sub("^(([^.]*\\.){2}[^.]*).*", "\\1", AreaCode1)))

```


```{r}
#ce <- mutate(ce, AreaCode = ifelse(substr(CEarea, 1, 4) == "27.3", substr(CEarea, 1, 9), sub("^(([^.]*\\.){2}[^.]*).*", "\\1", CEarea)))

# TODO - This assumption
# Filter out records with very low number of trips
#cef <- filter(ce, CEnumberOfFractionalTrips > 0.1)
# quantile(ce$CEnumberOfFractionalTrips, probs = seq(0, 1, by = 0.1), na.rm = TRUE)
# quantile(ce$CEnumberOfDominantTrips, probs = 0.95, na.rm = TRUE)
# hist(ce$CEnumberOfDominantTrips, breaks = 1000, xlim = c(0,200))
# hist(log10(ce$CEofficialDaysAtSea + 0.01), breaks = 100)
# #
# ggplot(ce, aes(CEnumberOfDominantTrips,CEnumberOfFractionalTrips )) +
#   geom_point()
#cef <- distinct(cef, AreaCode, CEmetier6)
#cef <- mutate(cef, GearGroup = vapply(CEmetier6, classify_gear, character(1)))

```


```{r}
med <- filter(d2div, AreaCode_system == "GSA")
# Slovenia is grouped with ICES area codes need to fix: Done
nor <- filter(d2div, !AreaCode_system == "GSA")
```

## ICES

```{r}
# Determine sampling schemes with logbooks monitoring method
d4oldmm <- filter(d4old, `Monitoring method` %in% "Logbook") # old dataset only one and removed either way due to NAs in almost all other variables
d4mm <- filter(d4, MonitoringMethod %in% "LB")  # Estonia
remLB <- unique(d4mm$SamplingScheme)
```


### Coverage by year


```{r, fig.dim= c(16, 12)}

current_year <- year(Sys.Date())

# Factors to be plotted in order
dfnor <- nor  %>%
  mutate(AreaCode2 = factor(AreaCode, levels = unique(ices_divisions$division)),
         GearGroup1 = factor(GearGroup, levels = c("DemTrawl", "DemSeine","Gillnetters", "LinesHooks", "PelSeine", "PelTrawl", "Others")))

# Remove NAFO areas
dfnor <- filter(dfnor, !is.na(AreaCode2))

# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoYears = length(unique(Year)))

# Without 0's
yearsCellWTZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  filter(is.na(NoTripsSampled) == F) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoYears = length(unique(Year)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoYears))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Years") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique year coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoYears))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Years", alpha = 0.85) +
  scale_x_discrete(labels = c("Demersal Trawl", "Demersal Seine", "Gilnetters", "Lines and Hooks", "Pelagic Seine", "Pelagic Trawl", "Other"))+
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Years of coverage by gear group and ICES division (2017-2024)"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

Fig3 <- b

ggsave("Fig3.png", Fig3, width = 20, height=16.5, units=c("cm"), dpi=300)
#grid.arrange(a, b, ncol=2)

```


### Coverage by sampling scheme


```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))

# Without 0's
yearsCellWTZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```

### Coverage by sampling effort
```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))

# Without 0's
yearsCellWTZ <- dfnor %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled )) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```

### Comparison with CE

```{r, fig.dim= c(16, 12)}
dfnornew <- filter(dfnor, Source %in% "2025DC") %>%
  filter(Year >= 2021 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0)
cemerg <- left_join(cef, dfnornew, by = c("AreaCode" = "AreaCode2", "GearGroup" = "GearGroup1"))

cefin <- distinct(cemerg, AreaCode, GearGroup, .orig_row) %>%
  mutate(Sampled = ifelse(is.na(.orig_row), "No", "Yes")) %>%
  distinct(AreaCode, GearGroup, Sampled) %>%
   mutate(GearGroup = factor(GearGroup, levels = c("DemTrawl", "DemSeine","Gillnetters", "LinesHooks", "PelSeine", "PelTrawl", "Others")),
          AreaCode = factor(AreaCode, levels = unique(ices_divisions$division)))


ggplot(cefin , aes(x = GearGroup, y = AreaCode, fill = Sampled)) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "SAmpled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Year * gear combination sampled"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```



## Med

### Coverage by year

```{r, fig.dim= c(16, 12)}

# Factors to be plotted in order
dfmed<- med  %>%
  mutate(AreaCode2 = factor(AreaCode, levels = paste0("GSA ", seq(1:30))),
         GearGroup1 = factor(GearGroup, levels = c("DemTrawl", "DemSeine","Gillnetters", "LinesHooks", "PelSeine", "PelTrawl", "Others")))

# Remove NAFO areas
dfmed <- filter(dfmed, !is.na(AreaCode2))

# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  filter(is.na(GearGroup1) == F) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoYears = length(unique(Year)))

# Without 0's
yearsCellWTZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(is.na(GearGroup1) == F) %>%
  filter(NoTripsSampled != 0) %>%
  filter(is.na(NoTripsSampled) == F) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoYears = length(unique(Year)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoYears))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Years") +
  labs(
    x = "Gear",
    y = "GSA",
    title = "Unique year coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoYears))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Years", alpha = 0.85) +
  scale_x_discrete(labels = c("Demersal Trawl", "Demersal Seine", "Gilnetters", "Lines and Hooks", "Pelagic Seine", "Pelagic Trawl", "Other"))+
  labs(
    x = "Gear group",
    y = "Geographical sub-area (GSA)",
    title = "Years of coverage by gear group and GFCM geographical sub-area (2017-2024)"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

Fig4 <- b

grid.arrange(a, b, ncol=2)

Fig4

ggsave("Fig4.png", Fig4, width = 20.5, height = 10, units = "cm", dpi = 300)
```

### Coverage by sampling scheme

```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% # 2017 - 2024
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))

# Without 0's
yearsCellWTZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>%
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoSampScheme = length(unique(SamplingScheme)))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "GSA",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = factor(NoSampScheme ))) +
  geom_tile(color = "white") +
  scale_fill_viridis_d(name = "Number of Sampling schemes") +
  labs(
    x = "Gear",
    y = "GSA",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```


### Coverage by sampling effort

```{r, fig.dim= c(16, 12)}
# With zeros - NAs are created by expanding the df
# These have been left in - Need to check if they correspond to 0 trips sampled
yearsCellWZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))

# Without 0's
yearsCellWTZ <- dfmed %>%
  filter(Year >= 2017 & Year < 2025) %>% #
  filter(!SamplingScheme %in% remLB) %>%
  filter(NoTripsSampled != 0) %>%
  group_by(AreaCode2, GearGroup1) %>%
  summarise(NoTripsSampled = sum(NoTripsSampled, na.rm = TRUE))


a <- ggplot(yearsCellWZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled )) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling schme coverage by gear and ICES area incl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

b <- ggplot(yearsCellWTZ, aes(x = GearGroup1, y = AreaCode2, fill = NoTripsSampled)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(name = "Number of trips sampled") +
  labs(
    x = "Gear",
    y = "ICES area",
    title = "Unique sampling scheme coverage by gear and ICES area excl 0 sampled trips"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(a, b, ncol=2)
```


```{r}
d4samType <- d4 %>%
  group_by(SamplingScheme,MonitoringMethod) %>%
  summarise(Samname = paste0(unique(SamplingSchemeType), collapse = ","))

```

#Some general patterns over time

```{r}
#calculate range of programs
#use only data from this year's call
d4e <- d4 %>%
  mutate(End_year = replace(End_year, is.na(End_year) == T,2025)) %>%
  mutate(End_year = replace(End_year, End_year == 2026 | End_year == 2027, 2025)) %>%
  mutate(range = End_year - Start_year) %>%
  mutate(Start_year = replace(Start_year, Start_year <2017, 2016)) %>%
  mutate(range = End_year - Start_year +1) %>%
  mutate(Start_year = replace(Start_year, Start_year <2017, "<2017"))

#filter for unique programs
d4_unique <- d4e %>% dplyr::select(Start_year,End_year,SamplingScheme,range, SamplingSchemeType,MonitoringMethod, AreaCode, TargetPopulation) %>%
  distinct()

#histogram of program lengths
ggplot(d4e)+
  geom_bar(aes(range, fill = SamplingSchemeType), color = "darkgrey",stat = "count")+
  labs(x = "Number of years", y = "Number of programmes", title = "Duration of bycatch monitoring programmes")+
  scale_y_continuous(expand = c(0,0))+
  theme_classic()


# #pull out columns of interest
# d4e_sub <- d4 %>%
#   filter(!MonitoringMethod == "LB") %>%
#   mutate(End_year = replace(End_year, is.na(End_year) == T,2025)) %>%
#   mutate(End_year = replace(End_year, End_year == 2026 | End_year == 2027, 2025)) %>%
#   filter(Start_year > 2016) %>%
#   mutate(range = End_year - Start_year +1) %>%
#   dplyr::select(Start_year,End_year,SamplingScheme,range, SamplingSchemeType,MonitoringMethod,AreaCode)

#expanded data frame for each year
# d4_byyear <- c()
# for(i in 1:length(d4e_sub$Start_year)) {
#   program <- d4e_sub[i,] #pull out unique program
#   temp <- as.data.frame(matrix(ncol = ncol(d4e_sub) + 1,nrow = program$range))
#   colnames(temp) <- c(colnames(d4e_sub),"Year")
#   temp$Year <- seq(program$Start_year,program$End_year,1)
#   temp[,1:ncol(d4e_sub)] <- program
#   d4_byyear <- rbind(d4_byyear,temp)
# }
#
# #time series of program type by monitoring method
# #MINDFUL THAT WE KNOW THERE ARE ZEROS! Probably not good to do this
# d4_byyear %>%
#   #filter(zero == "no") %>%
# ggplot() +
#   geom_bar(aes(x = Year, fill = MonitoringMethod), position = "stack") +
#   scale_x_continuous(breaks = seq(2017,2025, by = 1), expand = c(0,0)) +
#   scale_y_continuous(expand = c(0,0))+
#   theme_classic()

#time series of program type by program type
# d4_byyear %>% filter(zero == "no") %>%
# ggplot() +
#   geom_bar(aes(x = Year, fill = SamplingSchemeType), position = "stack") +
#   scale_x_continuous(breaks = seq(2017,2025, by = 1), expand = c(0,0)) +
#   scale_y_continuous(expand = c(0,0))+
#   theme_classic()

labels <- c("<2017", seq(2017,2025, by = 1))

#time series of programs by type and start year
Fig1 <- ggplot(data = d4e) +
  geom_bar(aes(x = Start_year, fill = SamplingSchemeType), position = "stack", color = "black") +
  scale_x_discrete(breaks = labels) +
  scale_fill_okabe_ito(alpha = 0.75)+
  scale_y_continuous(expand = c(0,0))+
  labs(x = "Initial year", y = "Number of programmes", fill = "Programme Type")+
  theme_classic()


Fig1

ggsave("Fig1.png", Fig1, width = 20, height=10, units=c("cm"), dpi=300)

#time series of programs bysea_star#time series of programs by method and start year
Fig2<- ggplot(data = d4e) +
  geom_bar(aes(x = Start_year, fill = MonitoringMethod), position = "stack", color = "black") +
  scale_x_discrete(breaks = labels) +
  #scale_fill_viridis_d(direction = -1)+
  scale_fill_okabe_ito(alpha = 0.75)+
  scale_y_continuous(expand = c(0,0))+
  labs(x = "Initial year", y = "Number of programmes", fill = "Method")+
  theme_classic()

Fig2

ggsave("Fig2.png", Fig2, width = 20, height=10, units=c("cm"), dpi=300)

```
#Percentage of programs with Sci. Observers
```{r}
#percentage of programs with SO
so <- length(which(d4e$MonitoringMethod %in% c("SO","SO~PO","SO~VO")))
so/length(d4e$MonitoringMethod)

#number of countries utilizing EM
em <- d4e %>% filter(MonitoringMethod == "EM") %>%
  select(Country) %>%
  distinct()
```
#Exclusion criteria
```{r}
#looking at exclusion criteria
exclusion <- d4e %>% filter(ExclusionFlag == "Y") %>%
  filter(is.na(ExclusionCriteria) == F) %>%
  mutate(ExclusionCriteria = replace(ExclusionCriteria, ExclusionCriteria == "low fishing effort", "Low fishing effort")) %>%
  mutate(ExclusionCriteria = replace(ExclusionCriteria, ExclusionCriteria == "Vessel space limitation~Uncooperative vessel", "Uncooperative vessel~Vessel space limitation")) %>%
  mutate(ExclusionCriteria = replace(ExclusionCriteria, ExclusionCriteria == "Small vessel size~Vessel space limitation~Low fishing effort", "Small vessel size~Low fishing effort~Vessel space limitation"))

Fig7 <- ggplot(data = exclusion) +
  geom_bar(aes(x= "", fill = ExclusionCriteria), color = "black")+
  labs(fill = "Exclusion Critera")+
  coord_polar("y", start = 0)+
  scale_fill_okabe_ito(alpha = 0.75)+
  theme_void()

Fig7

ggsave("Fig7.png", Fig7, width = 20, height=8, units=c("cm"), dpi=300)

#curious about how many exclusions relate to uncooperative
length(which(exclusion$ExclusionCriteria %in% c("Uncooperative vessel", "Uncooperative vessel~Vessel space limitation", "Uncooperative vessel~Small vessel size")))
```

#Sampling protocols (species sampled)
```{r}
#looking at sampling protocols
d4e <- d4e %>% filter(!MonitoringMethod == "LB")
Fig5a <- ggplot(data = d4e) +
  geom_bar(aes(x= "", fill = SamplingProtocol), color = "black")+
  scale_fill_okabe_ito(alpha = 0.75, order = c(7:9,1:6))+
  coord_polar("y", start = 0)+
  labs(fill = "Sampling Protocol")+
  theme_void()

#proportion that sample 'All' and 'Protected Species'
length(which(d4$SamplingProtocol == "All"))/length(d4$SamplingProtocol)
length(which(d4$SamplingProtocol == "ProtectedSpecies"))/length(d4$SamplingProtocol)

Fig5b <- ggplot(data = d4e) +
  geom_bar(aes(x=SamplingSchemeType, fill = SamplingProtocol),position = "fill", show.legend = F, color = "black") +
  scale_x_discrete(expand = c(0,0)) +
 scale_fill_okabe_ito(alpha = 0.75, order = c(7:9,1:6))+
  scale_y_continuous(expand = c(0,0))+
  labs(y = "Proportion", x= "Programme Type")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust = 1))

specific <- d4e %>% filter(!SamplingProtocol %in% c("All", "ProtectedSpecies", "Fish~ProtectedSpecies", "ProtectedSpecies~Elasmobranchs")) %>%
  count(SamplingProtocol)

Fig5 <- Fig5a + Fig5b + plot_annotation(tag_levels = "A")

Fig5

ggsave("Fig_5.png", Fig5, width = 25, height = 10, units = "cm", dpi = 300)
```
#Monitoring coverage
```{r}
#exclude logbook programs
lb <- d4 %>% filter(MonitoringMethod == "LB")
#look at monitoring coverage relative to thresholds
hist <- d2 %>% mutate(prop = NoTripsSampled / NoTripsTotal) %>%
  filter(!SamplingScheme %in% lb$SamplingScheme) %>%
  filter(prop > 0 & prop <1)

Fig8 <- ggplot(data = hist) +
  geom_histogram(aes(x=prop), fill = "lightgrey", color = "black", binwidth = 0.01) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0))+
  geom_vline(xintercept=0.01, color="orange", linetype = "dashed", linewidth = 1)+
  annotate(x= 0.01, y=+Inf,label = "0.01",vjust = 7, hjust=-0.0001, geom = "label", color = "orange", size = 11/.pt)+
   geom_vline(xintercept=0.1, color="maroon", linetype = "dashed", linewidth = 1)+
  annotate(x= 0.1, y=+Inf,label = "0.1",vjust = 7, hjust=-0.0001,geom = "label", color = "maroon",size = 11/.pt)+
   labs(x = "Proportion", title = "Proportion of fishing trips sampled (2022-2025)", y = "Number of programmes") +
  theme_classic()
Fig8

ggsave("Fig8.png", Fig8, width = 20, height = 10, units = "cm", dpi = 300)

#what % of schemes are below 10% threshold
length(which(hist$prop < 0.1)) / length(hist$prop)

#what % of schemes are below 0.1% threshold
length(which(hist$prop < 0.001)) / length(hist$prop)

#what % of schemes are below 10% threshold
length(which(hist$prop < 0.01)) / length(hist$prop)

#how does prop relate to total trips
ggplot(data = hist) +
  geom_point(aes(y= NoTripsTotal, x= prop))
```

Programs that report zeros

```{r}
#noticed a lot of NAs as well
d2e <- d2e %>% mutate(NoTripsSampled = replace(NoTripsSampled, is.na(NoTripsSampled) == T, 0))

zeros <- d2e %>% filter(NoTripsSampled == 0)

#plot by year and by country
#France mostly!
ggplot(data = zeros) +
  geom_bar(aes(x = Year, fill = Country))


#are there cases where a program reports zeros in a year
#Yes, 84 instances
trips_annual <- d2e %>% group_by(SamplingScheme,Year) %>%
  mutate(annual_trips = sum(NoTripsSampled)) %>%
  dplyr::select(SamplingScheme,Year,annual_trips,Country) %>%
  distinct()

zeros <- zeros %>% mutate(unique_ID = paste(SamplingScheme,AreaCode,Year, sep = "_"))

d4_byyear <- d4_byyear %>% mutate(unique_ID = paste(SamplingScheme,AreaCode,Year, sep = "_"))

d4_byyear <- d4_byyear %>% mutate(zero = ifelse(unique_ID %in% zeros$unique_ID, "yes","no"))

```

#Perceived importance issues
```{r}
#mean range of CF vs. IB
#function to pull last two letters (=CF or IB)
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

#classify by either CF or IB
d4e <- d4e %>% mutate(SST = substrRight(SamplingSchemeType,2))

d4_importance <- d4e %>% group_by(SST) %>%
  mutate(Mammals = mean(ImportanceMammals), Birds = mean(ImportanceBirds), Fish = mean(ImportancePETfish), Elasmobranchs = mean(ImportanceElasm), Reptiles = mean(ImportanceRept)) %>%
  dplyr::select(SST, Mammals, Birds, Fish, Elasmobranchs, Reptiles) %>% distinct()

d4_importance <- pivot_longer(d4_importance, !SST, names_to = "Taxon", values_to = "Importance")

Fig6<- ggplot(data = d4_importance) +
  geom_bar(aes(x = Taxon, y = Importance, fill = SST), stat = "identity", position = "dodge", color = "black") +
  labs(x = "", y = "Average perceived importance (0-4)", title = "Perceived importance of fishery monitored, relative to other fisheries, for the bycatch of different taxonomic groups", fill = "Sampling Scheme Type") +
  scale_fill_okabe_ito(alpha = 0.75,labels = c("Commercial fisheries", "Incidental bycatch"))+
  #scale_fill_discrete(palette = c(pal[6],pal[5]),labels = c("Commercial fisheries", "Incidental bycatch"))+
  scale_y_continuous(expand = c(0,0))+
  theme_classic()

Fig6

ggsave("Fig6.png", Fig6, width = 25, height = 10, units = "cm", dpi = 300)
```

#Part observed
```{r}
part_observed <- d4 %>% group_by(PartObserved) %>% tally()
length(which(grepl("So", d4$PartObserved) == T))

```
